Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-11 related.tex
editing related

\section{Related Work {\color{red} NOT EDITABLE}}\label{sec:related}

Attempting to model and characterize predictability is a very old problem which arguably began with Yule in 1927 when he invented AR and many attempts to quantify predicatbility have followed including ....

@@

>>>>

\section{Related Work }\label{sec:related}
{\color{red}[[NOT EDITABLE]]}
Attempting to model time series for prediction is an  old problem which arguably began with Yule in 1927 when he invented autoregression \cite{Yule27}. Since then hundreds if not thousands of prediction strategies have been developed for a wide variety of prediction tasks. The purpose of this paper is \emph{not} to model a time series for prediction but to understand the predictability of a real-valued-scalar time series model free and then to associate the model accuracy with the time series inherent complexity.

Quantifying predictability or sometimes called predicting predictability is also not a new problem and most solutions fall into two categories: model based and model free where information content is estimated through binning.

The first class of methods is model oriented. These methods often include one of two things: Building local  models around points in a time series or analyzing statistics on the distribution of model errors. A few examples of the first case are \cite{Smith199250,dvsplots}, in \cite{Smith199250} for example they build local error distributions around "landmarks"(look up actual word they use) of a reconstructed trajectory of a dynamical system. They then use these distributions to predict error bounds on  predictions which occur within that $\epsilon$-ball. DVS-plots (Deterministic-vs-Stochastic plots) are somewhat similar to this

@@

 and many attempts to quantify predicatbility have followed including ....
